### 2016-11-01 ms/ms.tex
made claire's edits

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.653 \pm 0.225$, $p$-value=$0.009$;
slope of closeness centrality variability and degree, $0.008 \pm
0.002$, $p$-value=$0.002$). In addition, plant persistence and degree
were not significantly related to network position variability
(Fig.~\ref{fig:cv}, estimate of the slope of closeness variability and
persistence $\pm$ SE, $-2.063 \pm 3.091$, $p$-value=$0.5$; slope of
closeness variability and degree, $0.0018 \pm 0.002$,
$p$-value=$0.3$). The variability of species network position was not
the result of closeness linearly increasing through time, and, in
fact, plant and pollinator closeness decreased slightly through time
(Fig.~S2, estimate of the slope of closeness through time $\pm$ SE,
pollinators: $-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants
$-0.007 \pm 0.001$, $p$-value=$1.4*10^{-6}$). Through statistically
significant, the slopes are so slight they may not be biologically
significant.

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). All of the networks
were significantly nested ($z$-scores $>$ 2,
Fig.~\ref{fig:baci}). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from zero (estimate
of the slope of modularity through time $\pm$ standard error of the
estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). In addition,
none of the networks were significantly modular ($z$-scores $<$ 2,
Fig.~\ref{fig:baci}). Connectance decreased as the community assembled
(Fig.~\ref{fig:baci}, estimate of the slope of connectance through
time $\pm$ standard error of the estimate, $-0.0434$ $\pm$ $0.0152$,
$p$-value=$0.03$). Specialization also decreased, though the slope was
only marginally significantly different from zero (estimate of the
slope of specialization through time $\pm$ SE, $-0.926$ $\pm$ $0.450$,
$p$-value=$0.078$). Most communities were more generalized than
expected when interactions were randomized (Fig.~\ref{fig:baci}).

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species were removed incrementally by degree (estimate
of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
4*10^{-3}$, $p$-value=$0.987$) or abundance ($0.001 \pm 0.003$,
$p$-value=$0.65$). In contrast, the sensitivity of networks to
cascading perturbations, as measured by the algebraic connectivity of
the network, increased as the network assembled (Fig.~\ref{fig:rob},
estimate of the slope of sensitivity to cascading perturbations
through time $\pm$ SE, $0.6814 \pm 0.272$, $p$-value=$0.042$).

>>>>

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.653 \pm 0.225$, $p$-value=$0.009$;
slope of closeness centrality variability and degree, $0.008 \pm
0.002$, $p$-value=$0.002$). The slope of these relationships remained
significant when the species with the top $10$ persistence and degree
scores were dropped. In addition, plant persistence and degree were
not significantly related to network position variability
(Fig.~\ref{fig:cv}). % estimate of the slope of closeness variability and
% persistence $\pm$ SE, $-2.063 \pm 3.091$, $p$-value=$0.5$; slope of
% closeness variability and degree, $0.0018 \pm 0.002$,
% $p$-value=$0.3$).
The variability of species network position was not the result of
closeness linearly increasing through time, and, in fact, plant and
pollinator closeness decreased slightly through time (Fig.~S2,
estimate of the slope of closeness through time $\pm$ SE, pollinators:
$-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants $-0.007 \pm
0.001$, $p$-value=$1.4*10^{-6}$). Through statistically significant,
the slopes are so slight they may not be biologically significant.

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). All of the networks
were significantly nested ($z$-scores $>$ 2,
Fig.~\ref{fig:baci}). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from
zero. % (estimate
% of the slope of modularity through time $\pm$ standard error of the
% estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$).
In addition, none of the networks were significantly modular
($z$-scores $<$ 2, Fig.~\ref{fig:baci}). Connectance decreased as the
community assembled (Fig.~\ref{fig:baci}, estimate of the slope of
connectance through time $\pm$ standard error of the estimate,
$-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). Specialization also
decreased, though the slope was only marginally significantly
different from zero (estimate of the slope of specialization through
time $\pm$ SE, $-0.926$ $\pm$ $0.450$, $p$-value=$0.078$). Most
communities were more generalized than expected when interactions were
randomized (Fig.~\ref{fig:baci}).

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species were removed incrementally by
degree % (estimate
% of the slope of robustness through time $\pm$ SE, $6*10^{-5} \pm
% 4*10^{-3}$, $p$-value=$0.987$)
or abundance. % ($0.001 \pm 0.003$,
% $p$-value=$0.65$)
In contrast, the sensitivity of networks to
cascading perturbations, as measured by the algebraic connectivity of
the network, increased as the network assembled (Fig.~\ref{fig:rob},
estimate of the slope of sensitivity to cascading perturbations
through time $\pm$ SE, $0.6814 \pm 0.272$, $p$-value=$0.042$).
